Determinism, Complexity, and Predictability in Computer Performance

### 2014-01-06 pecomplexity.tex
Updating some Prediction Figures
add author info

\documentclass{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{letterpaper}                   % ... or a4paper or a5paper or ...
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parIEEEabrvskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}
\usepackage{amsthm}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

@@

@@

\begin{figure}
        \centering
        \begin{subfigure}{\textwidth}
                \includegraphics[width=\textwidth]{figs/colfullts}
                \caption{col IPC  Full Time Series}
                \label{fig:gull}
        \end{subfigure}%
        \newline
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{figs/colshortts}
                \caption{col IPC  Short Time Series for structure illustration}
                \label{fig:svdFullColored}
        \end{subfigure}
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
         \caption{col  Time Series }\label{fig:svdFull}
\end{figure}

@@

%\bibliographystyle{}
\bibliography{bibliofile}

>>>>

\documentclass{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{letterpaper}                   % ... or a4paper or a5paper or ...
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parIEEEabrvskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}
\usepackage{amsthm}
\usepackage{authblk}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

@@

\author[1]{Joshua Garland \thanks{joshua.garland@colorado.edu}}
\author[1]{Ryan James \thanks{ryan.james@colorado.edu}}
\author[1,2]{Elizabeth Bradley \thanks{lizb@colorado.edu}}
\affil[1]{Department of Computer Science \\
  University of Colorado at Boulder \\
  Colorado, USA
}
\affil[2]{Santa Fe Institute \\
  New Mexico, USA
}

@@

\begin{figure}
        \centering
        \begin{subfigure}{\textwidth}
                \includegraphics[width=\textwidth]{figs/svdPrediction}
                \caption{SVD LMA Prediction}
                \label{fig:gull}
        \end{subfigure}%
        \newline
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{figs/svdPredictionFull}
                \caption{SVD LMA Prediction with Full Time Series}
                \label{fig:svdFullColored}
        \end{subfigure}
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
         \caption{SVD LMA Prediction Figures }\label{fig:svdFull}
\end{figure}

\begin{figure}
        \centering
        \begin{subfigure}{\textwidth}
                \includegraphics[width=\textwidth]{figs/colfullts}
                \caption{col IPC  Full Time Series}
                \label{fig:gull}
        \end{subfigure}%
        \newline
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{figs/colshortts}
                \caption{col IPC  Short Time Series for structure illustration}
                \label{fig:svdFullColored}
        \end{subfigure}

        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
         \caption{col  Time Series }\label{fig:svdFull}
\end{figure}

\begin{figure}
        \centering
        \begin{subfigure}{\textwidth}
                \includegraphics[width=\textwidth]{figs/colPredShortTS}
                \caption{col IPC  Full Time Series}
                \label{fig:gull}
        \end{subfigure}%
        \newline
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{figs/colPredfullTS}
                \caption{col IPC  Short Time Series for structure illustration}
                \label{fig:svdFullColored}
        \end{subfigure}

        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
         \caption{col\_major Predictions }\label{fig:svdFull}
\end{figure}

@@

\bibliographystyle{unsrt}
\bibliography{bibliofile}
